Manuscript

### 2017-07-15 manuscript.Rmd
Fix impacts analysis
The impacts analysis relies on draws from the analytical Hessian matrix of the model. The problem is that the Hessian in spatial models is often close to singular, which means it cannot be inverted. spdep gets around this by using a numerical Hessian instead if the inversion fails (this is the warning that you get when you estimate the SDM).

The problem is that then the object that the impacts needs isn't there. So I've tightened the convergence tolerance on the estimation, and everything works. I've also added a helper function to process the impacts statistics in a bett

# source functions
source("R/logsums.R")

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
regression_data[[2]]["park_ls"] <- calculate_park_logsums(
  boston_tracts, boston_parks, betas = c(.00001, -30))
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed")
  })

@@

mc_impacts <- lapply(base_sdm, function(dv){
  # TODO
  impacts <- lapply(seq_along(1:1), function(i) {
    impacts(dv[[i]], tr = tr_mc[[i]])
  })

  names(impacts) <- cities[i]

>>>>

# source functions
source("R/logsums.R")
source("R/impact_summary.R")

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
regression_data[[2]]["park_ls"] <- calculate_park_logsums(
  boston_tracts, boston_parks, betas = c(.00001, -30))
regression_data[[3]]["park_ls"] <- calculate_park_logsums(
  nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

  # TODO update when more cities are available
  models <- lapply(seq_along(1:1), function(city){
    lagsarlm(this_formula, data = regression_data[[city]],
             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed",
             tol.solve = 1e-16)
  })

@@

mc_impacts <- lapply(base_sdm, function(dv){
  # TODO
  impacts <- lapply(seq_along(1:1), function(i) {
    impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
  })

  names(impacts) <- cities[1]
